Containers and R: the Rockerverse and beyond

### 2019-09-09 manuscript.Rmd
add notes from #5
minor fix for liftr

In summary, _liftr_ tries to redefine the meaning of computational reproducibility by offering system-level reproducibility for data analysis.
It provided a practical way for achieving it --- a new perspective on how reproducible research could be done in reality.
Further, sharing system environments for data analysis also becomes extremely easy, since users only need to share the R Markdown document (with a few extra metadata fields), and compile them with _liftr_.
As an example, _liftr_ demonstrated its advantage for R Markdown-based computational workflow orchestration, by effortlessly containerizing 18 complex Bioconductor workflows in the DockFlow project (https://dockflow.org) in 2017.

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}.
CB ..
RC ..
DE ..
ME ..
CF ..
BW ..
KR ..
NR ..
NX ..
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.

>>>>

In summary, _liftr_ tries to redefine the meaning of computational reproducibility by offering system-level reproducibility for data analysis.
It provided a practical way for achieving it --- a new perspective on how reproducible research could be done in reality.
Further, sharing system environments for data analysis also becomes extremely easy, since users only need to share the R Markdown document (with a few extra metadata fields), and compile them with _liftr_.
As an example, _liftr_ demonstrated its advantage for R Markdown-based computational workflow orchestration, by effortlessly containerizing 18 complex _Bioconductor_ workflows in the DockFlow project (https://dockflow.org) in 2017.

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}.
CB ..
RC ..
DE ..
ME ..
CF ..
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.
